PANCHANGE_data_preprocessing

### 2020-12-03 PANCHANGE_data_preprocessing2020-07-15.Rmd

---
title: "PANCHANGE_data_preprocessing"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: Sys.Date()
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

@@

# Specify cohort
```{r Specify cohort}
GLAD = TRUE
EDGI = FALSE
NBR = FALSE
RAMP = FALSE
GLAD_and_EDGI = FALSE
```

>>>>

---
title: "PANCHANGE_data_preprocessing"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

@@

# Specify cohort
```{r Specify cohort}
GLAD = FALSE
EDGI = FALSE
NBR = FALSE
RAMP = FALSE
GLAD_and_EDGI = TRUE
```
